### 2016-05-21 Paper/paper.tex
methods written

\begin{figure}[h!]
	\label{fig: fig4}
  \centering
    \includegraphics[width=\textwidth]{ReplicatedFigures/fig4.pdf}
        \caption{Periodograms of the time series sections colored blue and green in Figure ~\ref{fig: fig1}. The black line denotes the inertial frequency.   The dotted lines on the left figure indicates the location of the eddy peak and the expected shift in the inertial frequency. The semi-parametric model fit on the section of the data used in fitting the model is highlighted green on the left figure and blue on the right figure. The red dotted line indicates the model fit extended beyond the frequencies where it was fit. }
\end{figure}

>>>>

\begin{figure}[h!]
	\label{fig: fig4}
  \centering
    \includegraphics[width=\textwidth]{ReplicatedFigures/fig4.pdf}
        \caption{Periodograms of the time series sections colored blue and green in Figure ~\ref{fig: fig1}. The black line denotes the inertial frequency.   The dotted lines on the left figure indicate the location of the eddy peak and the expected shift in the inertial frequency. The semi-parametric model fit for the frequencies used in model fitting is highlighted green on the left figure and blue on the right figure. The red dotted line indicates the model fit extended beyond the frequencies where it was fit. }
\end{figure}
